\documentclass[12pt]{letter}

\usepackage[american]{babel}
\renewcommand{\baselinestretch}{1.2}   % double spaces a document
\usepackage[usenames]{color}
\newcommand{\dpf}[1]{\noindent{\textcolor{Blue}{\{{\bf dpf:} \em #1\}}}}
 
\setlength{\topmargin}{0in}         % 1 in top/bottom
\setlength{\headheight}{0.25in}
\setlength{\headsep}{0.25in}
\setlength{\textheight}{8.0in}
\setlength{\oddsidemargin}{0.0in}   % 1. in left/right
\setlength{\textwidth}{6.5in}
\pagestyle{empty}  % so no page numbers

\begin{document}

\noindent
July 24, 2007

\vspace{0.3in}

\noindent
Professor A. T. A. Wood\\
School of Mathematical Sciences \\
University of Nottingham \\
University Park \\
Nottingham NG7 2RD \\  
United Kingdom

\vspace{0.3in}

\noindent
Dear Professor Wood: 

\noindent
Please find attached our revision to

\noindent
{\bf JRSSB submission B6215R}: ``Alpha investing: A procedure for sequential control of expected false discoveries'' (with Dean Foster)

\noindent
We have rewritten the paper to address the suggestions and comments.  First, as you may have noticed, we changed the title a little to clarify the topic of the paper and remove an acronym. Further changes emphasize a general tightening of the language that reduces the length to 26 pages.

We enclose a detailed response to the comments on the previous version,
starting with your comments, those of the AE, and then those of the referee.

\vspace{0.3in}
\noindent
Sincerely,
\vspace{0.3in}

\noindent
Robert A. Stine  \\
stine@wharton.upenn.edu



\newpage
\centerline{\bf Editor's report}

The revised paper is more concisely written, with a general reduction in length down to 26 pages (a bit less than requested).

{\bf Typos and minor}

We either fixed the mistakes or removed the sentences with the noted typos. As to the format of references, we use bibtex and a style file that alleges it produces an RSS citation.  We hope they look OK in this version.


\newpage
\centerline{\bf AE's report}

{\bf Major comment}

We shortened all of the sections of the paper. With regard to the suggested specific reductions,
\begin{enumerate}
 \item We reduced Section 5.1 and merged the results into the rest of Section 5.
 \item The former Section 7 is shorter with a more concise description of the examples 
          and now appears as Section 6.
 \item We removed the last two paragraphs, as suggested.
\end{enumerate}

{\bf Minor comments}

The citations now refer to the published papers.


\newpage
\centerline{\bf Response to referee}

\begin{description}

  \item[Justification of mFDR vs FDR] This preliminary comparison no longer appears.
  
  \item[Example in Section 7.2] We added two examples. One example directly compares    
         alpha-investing to the weighted BH procedure that uses an oracle to assign 
         weights (see Figure 2).  The second added example demonstrates the use
         of alpha-investing for a sequence of hypotheses (summarized in Figure 3).
         
   \item[Minor comments] \ \
      \begin{itemize}
        \item We consistently use the word ``uniform'' in the revision.
        \item We agree and have made Section 5.1 much more brief.
        \item We moved this paragraph into the concluding discussion.
      \end{itemize}
\end{description}

\newpage
\centerline{\bf Summary of Other Changes}

\begin{itemize}

  \item Merged the reduced Section 5 with Section 6.
  \item Removed former Theorem 3 and relegate these 
           tangental results to a remark at the end of Section 5.
  \item Removed distinct breaks for  subsections from the paper.
  \item Shortened section 7.1 (designing rules) and merged the discussion into the rest of
           Section 6 (in the new numbering).
  \item Added simulations that (a) compare alpha-investing to weighted BH and 
          (b) demonstrate that it works when applied to a sequence of hypotheses.

\end{itemize}

\end{document}  
